H2 Supplement

### 2023-02-06 H1.Rmd
created links to supplementary within the main results

We conducted a linear-mixed-effects model to test for gender differences in internalization when participants are nested within country. Our outcome measure was internalization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for gender,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between being female and higher internalization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
We conducted a series of independent-samples t-tests to test for gender differences in internalization across all countries.  We found significant gender differences in internalization across `r total_sig` countries. Of these, `r pos` were in the predicted direction, while in `r neg` countries (`r c1` and `r c2`), males showed higher internalization than females (see Supplementary Materials Table S_X).

@@

We conducted another linear-mixed-effects model to test for gender differences in symbolization when participants are nested within country. Our outcome measure was symbolization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for gender,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between being female and higher symbolization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
We conducted a series of independent-samples t-tests to test for gender differences in symbolization across all countries. We found significant gender differences in symbolization across `r total_sig` countries. Of these, `r pos` were in the predicted direction, while in `r neg` countries (`r c1` and `r c2`), males showed higher symbolization than females (see Supplementary Materials Table S_X).

>>>>

We conducted a linear-mixed-effects model to test for gender differences in internalization when participants are nested within country. Our outcome measure was internalization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for gender,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between being female and higher internalization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
We conducted a series of independent-samples t-tests to test for gender differences in internalization across all countries.  We found significant gender differences in internalization across `r total_sig` countries. Of these, `r pos` were in the predicted direction, while in `r neg` countries (`r c1` and `r c2`), males showed higher internalization than females (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Internalization_Table)).

@@

We conducted another linear-mixed-effects model to test for gender differences in symbolization when participants are nested within country. Our outcome measure was symbolization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for gender,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between being female and higher symbolization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
We conducted a series of independent-samples t-tests to test for gender differences in symbolization across all countries. We found significant gender differences in symbolization across `r total_sig` countries. Of these, `r pos` were in the predicted direction, while in `r neg` countries (`r c1` and `r c2`), males showed higher symbolization than females (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Symbolization_Table)).

### 2023-02-06 H2.Rmd
created links to supplementary within the main results

all_cor_rs <- function(c){
  c$estimate
}
rs_for_table <- lapply(all_cor_tests, all_cor_rs)
all_cor_ps <- function(c){
  c$estimate
}
ps_for_table <- lapply(all_cor_tests, all_cor_ps)
Ns_for_table <- lapply(x, N_fun)

@@

We conducted a linear-mixed-effects model to test if this relationship between age and internalization holds when participants are nested within country. Our outcome measure was internalization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
We conducted a series of correlations test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials Table S_X).

@@

Similarly, for symbolization, we conducted a linear-mixed-effects model to test if the relationship between age and symbolization holds when participants are nested within country. Our outcome measure was symbolization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
We conducted a series of correlations test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials Table S_X).

>>>>

all_cor_rs <- function(c){
  c$estimate
}
rs_for_table <- lapply(all_cor_tests, all_cor_rs)
all_cor_ps <- function(c){
  c$p.value
}
ps_for_table <- lapply(all_cor_tests, all_cor_ps)
Ns_for_table <- lapply(x, N_fun)

@@

We conducted a linear-mixed-effects model to test if this relationship between age and internalization holds when participants are nested within country. Our outcome measure was internalization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
We conducted a series of correlations test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Internalization)).

@@

Similarly, for symbolization, we conducted a linear-mixed-effects model to test if the relationship between age and symbolization holds when participants are nested within country. Our outcome measure was symbolization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
We conducted a series of correlations test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Symbolization)).

### 2023-02-06 supp_H2.Rmd
created links to supplementary within the main results

all_cor_rs <- function(c){
  c$estimate
}
rs_for_table <- lapply(all_cor_tests, all_cor_rs)
all_cor_ps <- function(c){
  c$estimate
}
ps_for_table <- lapply(all_cor_tests, all_cor_ps)
ps_output_for_table <- lapply((lapply(all_cor_tests, all_cor_ps)), ps)
Ns_for_table <- lapply(x, N_fun)

>>>>

all_cor_rs <- function(c){
  c$estimate
}
rs_for_table <- lapply(all_cor_tests, all_cor_rs)
all_cor_ps <- function(c){
  c$p.value
}
ps_for_table <- lapply(all_cor_tests, all_cor_ps)
ps_output_for_table <- lapply((lapply(all_cor_tests, all_cor_ps)), ps)
Ns_for_table <- lapply(x, N_fun)
